Turbulence in compact to giant HII regions

### 2022-04-08 strucfunc_paper.tex
Typo

In Appendix~\ref{sec:finite-box-effects} we consider the effects
on the structure function of the finite size \(L\) of the observational map.
If the true correlation length \(r_0\) is more than a small fraction of the map size
(approximately, \(r_0 > 0.1 L\)),
then the apparent velocity variance \(\sigma\pos^2\) measured directly from the data
is less than the true \(\sigma\pos^2\) of the underlying fluctuations
(see Figure~\ref{fig:finite-box-effect}).
This is because the observed map is not large enough to sample
the full range of velocity variations.
At the same time, the apparent correlation length \(r_0'\) is smaller
than the true value.

@@

In the next sections we discuss the application and interpretation of the turbulent parameters we obtained in our results.
We present a resume of the turbulence theory and its validation to \hii{} regions.
It is also mentioned some physical processes that contribute to stirring the ionized gas and the possibility that they are responsible for the observed velocity fluctuations.
We present the most important correlations between the turbulent parameters and physical properties of our \hii{} region sample and finally we discuss our results in the context of previous structure functions.

\subsection{Turbulence}\label{sec:turbulence-theory}

\textit{Will 2021-12-10: Moving this section to later for now. Maybe
  this material could go in discussion.}

The idea to treat the ionized regions from a fluid mechanic view is intuitive if we consider the continuum hypothesis. 
We validate this hypothesis using the Knudsen number defined as \(\text{Kn} \equiv \lambda / l\), where \(\lambda\) is the mean free path of the medium and \(l\) a characteristic length of the phenomenon we are studying.
Taking into account a \(\lambda_{\text{HII}}\) of \SI{2.7e-7}{pc} \citep{1941ApJ....93..369S} and a \(l_{\text{HII}}\) of \SI{1}{pc} for ionized regions we obtained \(\text{Kn} \approx 10^{-7}\), while in general the continuum approach is valid for \(\text{Kn}\ll 1\).

A turbulent behavior in the flows is more common in fluid systems than a laminar one.
These turbulent flows tends to be unsteady, irregular and chaotic, and the turbulent motions are observed in many scales. 
The turbulent flows are associated with a high Reynolds numbers which is defined as \(\text{Re} = l v_{l} / \nu \), where \(v_{l}\) is a characteristic velocity in the fluid system and \(\nu\) is the kinematic viscosity of the medium.
Experiments have shown that a flow which is laminar become turbulent when increasing the velocity (i.e., increasing the Re) and a large range of velocity fluctuation appear at all scales.
A high Re reflects high ratio of the advection/difussion terms of the Navier-Stokes equations, being interpreted as that the inertial forces taking over the viscous ones. 
Hence it is possible to assume that if viscosity is not dominant in a flow, this flow would be turbulent.

As astronomical observation made it possible to measure a large number of points with a high accuracy, it was found that velocities show a non-thermal component reflecting characteristic of turbulent earthly flows.
The existence of turbulent flows in astrophysical objects, ranging in scales from 10\(^6\) to 10\(^{17}\) m \citep{2010ApJ...710..853C} is thought to be consequence of the high \(Re\), between 10\(^4\) and 10\(^9\) \citep{1949ApJ...110..329C,lagrois2011} that characterized these objects.

The classic turbulence theory assumes a three-dimensional isotropic, incompressible and subsonic flow that can be described using an energy spectrum formed by vortices or eddies of different sizes \citep{kolm1}.
The concept of the energy spectrum assumes that the energy is cascading down inside the flow from the largest to the smallest scales.
The different scales in the energy cascade are defined based on their Re.
In one side of the spectrum there is the energy injection scale, \(L_I\), that is related to the largest vortices, called the integral scales, where \(\text{Re} \rightarrow \infty\).
On the other side of the spectrum there is the dissipation of energy at small scales, \(l_I\), where  \(\text{Re} \rightarrow 1\) and it is assumed that small vortices are responsible for the friction that dissipates the energy flux into thermal energy.
In between there is the inertial range, \(l_d  << l << L_I\), where in a stationary case the energy transfer is at a constant rate.

The rate of transfer of specific energy \(\epsilon\) (energy per unit mass) in the inertial range is independent of the \(l\) scale having the form \(\epsilon \sim v_l^2 / \tau_l\), where the kinetic energy is of the order of \( v_l^2\) and the life time of a velocity fluctuation is \(\tau_l\), which can be can be put in terms of \(\tau_l \sim l / v_l\). 
Hence we obtain \( v_l \sim (\epsilon l)^{1/3}\) where \(\epsilon\) is invariant in the cascade.

The energy cascade is described using the energy spectrum, $E(k) \propto k^{\beta}$ where \(k\) is the wave number for a determined scale \(l\) ($k \equiv l^{-1}$).
The total specific energy of a determined $l$ scale is of the order \(\langle v_{l}^{2} \rangle \) and is the energy integral above the associated \(k\), defined as:

\begin{equation}\label{eq:energy-spectrum}
 \langle v_{l}^{2} \rangle = \int_{k}^{\infty} E(k)dk
\end{equation}
%
If it is assumed that this energy is of the order of $(\epsilon l)^{\frac{2}{3}} \sim (\frac{\epsilon}{k})^{\frac{2}{3}}$ we can differentiate equation \ref{eq:energy-spectrum} and obtained the final form:

\begin{equation}\label{eq:kolmogorov-law}
E(k) \propto \epsilon^\frac{2}{3} k^{-\frac{5}{3}}
\end{equation}
%
where \(\beta = -5 / 3\) is the Kolmogorov law.
For supersonic turbulence the index is $\beta=-2$ \citep{burg}.

Using a statistical law that relates the moments \(M_n\) of order \(n\) with the increments in the velocity field for a separation \(\boldsymbol{r}\) \citep{Leqism}, we have:

\begin{equation}\label{eq:velocity-moments}
M_n = \langle \vert \boldsymbol{v}(\boldsymbol{x} + \boldsymbol{r})- \boldsymbol{v}(\boldsymbol{x})\vert^n \rangle \propto (\epsilon r)^{n/3}
\end{equation}
%
the average is over all the positions \(\boldsymbol{x}\) and directions \(\boldsymbol{r}\). 
The Kolmogorov model predicts that the moment of order 2, the second-order structure function (equation \ref{eq:Br}), follows \(M_2 \propto r^{2/3}\).

\subsection{Origins of interstellar turbulence}\label{sec:origins-turbulence}

In the particular case of GEHR, as supersonic motions dissipate energy by shocks in time scales relatively short compared with the age of the region, it is necessary an energy source to replenish continuously the energy lost. From the observed velocity  dispersion \(\sigma\), and assuming that we have an isotropic distribution of velocities,  we can estimate the 3D velocity dispersion by \(\sigma_\mathrm{3D} = \sqrt{3} \sigma\). The mass of the ionized gas together with the velocity dispersion \(\sigma_\mathrm{3D}\)  are used to estimate the kinetic energy in the GEHRs. As these objects have typically  masses of the ionized gas of \num{\sim e5} M\(_{\sun}\) and velocity dispersion values  of \SI{\sim 20}{km.s^{-1}} \citep{1984ApJ...287..116K}, typical kinetic energy of the ionized gas is \SI{\sim e51}{ergs}.

In the standard Kolmogorov model, the energy spectrum of turbulence becomes dependent only on \(\epsilon\), the mean dissipation of energy per unit time per unit mass of fluid,  with the inertial forces transferring without losses kinetic energy from larger to smaller turbulent elements within the inertial range. Let \(L_c\) be the characteristic length of the largest eddies, and \(\delta v\) the typical velocity.

We have then that \(\epsilon = (\delta v)^{3}/L\). In steady-state turbulence, equilibrium exists between the energy input and the energy dissipation rates. 
Although the present observations indicate that turbulence in \hii{} regions may not follow the Kolmogorov model, with energy input occurring at different scales, so that a  truly inertial range may not exist at all, lets us make a crude estimation of the  amount of energy transferred between scales using this simple model. 
Assuming the above figures for the mass of the gas and velocity dispersion, \(\delta v = \sigma_\mathrm{3D}\),  and a \(L_c\) of \SI{100}{pc}, we obtain that the energy transfer rate \SI{\sim e37}{erg.s^{-1}}, and  the time scale for energy transfer, \(L/\delta v \), would be of few million years.

There are several energy sources that could provide or contribute  to the energy required: of the order of kpc, the differential rotations of the galaxy that produces shear at large scale, at scales of the order of hundreds of pc, supernova explosions inject a large amount of kinetic energy.
At scales of several tens of pc the expansion of \hii{} regions and stellar winds are a source of energy and, bipolar flows, shocks, jets and champagne flows inject energy at small scales about one tenth of a pc.

The lack of precise information on how these mechanism contribute to the emission line broadening make a non-trivial task to determine at what extent they play a role in the interstellar turbulence, contributing to the complexity of the extraction of pure turbulent motions from velocity profiles in nebulae \citep{2011MNRAS.413..705L,arthur2016turbulence}.

@@

Ideally the correlation length \(r_0\) should represent the scale of dominant energy injection.
It is unclear what are the precise mechanisms driving the turbulence, thought a lot of options are candidates.
The most probable scenario is that the velocity fluctuations are consequence of the combination of various mechanism.
Many of these mechanisms, at some extent, affect all the \hii{} regions studied in this work.
We can use the kinematic analysis of the regions to investigate how previously identified energy injection mechanisms could be related to the correlation length.

\citet{2009AJ....137..367O} present a three-dimensional study of the dynamic structure of the Orion nebula.
The high-velocity stellar wind from \(\theta^1\) Ori C will confine the ionized gas, even the high ionization emission lines, to a thick shell.
In one direction, at a distance of \SI{0.1}{pc} from the massive star a stationary shell of shocked material is formed when the ram pressure of the photoevaportation flow balances the thermal pressure of the shocked wind.
In the other direction there is a free flow of the hypersonic wind.
At a smaller scale of \SI{0.02}{pc} there is an interaction between the closest proplyd photoevaporation flow and the stellar wind which results in bowshocks.
According to \citet{2001ApJ...561..830G} the influence of stellar wind interactions is restricted to the central 0.05 pc. 
Orion also present a champagne flow where the photoionized gas streams away from the ionization front covering a distance of \(\sim\)\SI{1}{pc} from the molecular cloud \citep{1973ApJ...183..863Z}.

Our correlation length results for the Orion Core and EON from table~\ref{tab:Res} despite been close to the scales mentioned above still aren't conclusive enough to determine a direct relation between them.
As mentioned in \citet{arthur2016turbulence} the mechanism mentioned in the previous paragraph would play a secondary role in stirring up the gas motions and it would be necessary to determine if the velocity fluctuations arise from pure turbulent motion inside the ionized clouds or a consequences of density and brightness fluctuations.

@@

\subsubsection{Structure function power-law index \(m\)}\label{sec:powe-index}

The index \(m\) shown in the last column of Table \ref{tab:Res} is used for comparison between observations and the theoretical value of 0.67 (equation \ref{eq:velocity-moments}).
All our indices are above this theoretical value and this is attributed to the fact that the \hii{} regions do not comply with the assumptions established in the development of the turbulent theory.

From section~\ref{sec:regions-milky-way} we know that most of all assumption mentioned in section~\ref{sec:turbulence-theory} are not meet for our \hii{} region sample.
\hii{} regions emerged from a molecular cloud with highly filamentary and clumpy density structure .
There is a large increase in the temperature because of the photoionization, and the density gradients with the pressure gradients accelerate the flow which occurs on multiple scales consequence of the fractal nature of the molecular cloud \citep{arthur2016turbulence}.
The radiation pressure, stellar winds and region expansion, among other physical processes would create pressure-driven shock waves propagating faster than the speed of sound in the medium.
This would make the flow compressible and supersonic in \hii{} regions.
Also, as \hii{} regions are three-dimensional objects our structure function results comes from a projection of this three-dimensional structure to a two-dimensional velocity field.
But despite the complex nature of \hii{} regions and observational limitations we obtain a common pattern for the structure function and the value of the power-law index falls in a certain limited range of values. 
The differences with respect the theoretical value are often used as a diagnostic tools to identify properties that are not consider in the assumptions of the turbulence theory.

To study the projection of a three-dimensional structure function to a two-dimensional structure function, known as projection smoothing \citep{von1951methode, munch1958internal,1987ApJ...317..686O}, relationships between the power-law indices were proposed:

@@

As a conclusion, if the extension of the HII region is compared with its depth (three-dimensional case) the value of the index is 1.6. 
While the case where the extension is much greater than its depth (two-dimensional case) the region will have a value of 0.6 .

The mean value \(m\) of our sample is \(\sim\)1. 
Following the equation \ref{eq:projection-smoothing-3d} the \hii{} regions in our sample with \(m >\) 1 would present a depth which is in the order of magnitude comparable to the length of the observed box size \(L\) been closest to this value as \(m\) tends to 1.6. 
On the other hand, \hii{} regions with values \(m <\) 1 would present a thinner structure as they tend to the value of 0.6.
This analysis should not be regarded as conclusive about the true structure of the regions and would require further observations with a combination of kinematics analysis to determine the best way to determine the depth of each region.
As we show in section \ref{sec:sigmapos-vs-sigmalos} the ratio between \(\sigma\pos\) and \(\sigma_{\text{los}}\) can also be used to give an idea of the depth o the region.

Deviations from the Kolmogorov model are expected in \hii{} regions as the photoionized flow in their interior has a different nature as the flows upon the theory is constructed. 
Also magnetic fields would play a very important role in the dynamics of the gas motions.
Despite these differences is clear that the self-similarity motions is a common behavior conserved at scales from parsecs to hundreds of parsecs. 
With the advanced of the observational capabilities with more computational power for a better understanding of turbulent motions the gap between theory and observations is hoped to be reduced.

@@

As a justification for the use of the structure function we can consider that any relation between the line width and line-of-sight depth can be interpreted in terms of a correlation between velocity spread and scale size.
If we have an optically thin spectral line where it will have a width which is related to the total radial velocity dispersion of all fluctuations sampled along the line-of-sight \citep{1984ApJ...277..556S}. 
The standard deviation of the velocity centroid, \(\sigma\pos\), and the mean non-thermal linewidth, \(\sigma_{\text{los}}\), allow us to compare the relation between the kinematical disorder on the plane-of-the sky and along the line-of-sight  \citep{2011MNRAS.413..705L}.
In these sense the structure function is used as a tool to investigate the projection of a three-dimensional correlation function onto the plane of sky \citep{arthur2016turbulence}.

We can consider as a main broadening mechanisms the kinematical disorder along the LOS related to velocity gradients by the clumpiness on the molecular cloud and turbulent movements.
On the plane-of-sky the consequences of those gradients and movements is measured in every pixel. 
The spatial variations on the velocity field would depend on the targeted pixel, depending on the motions inside the cloud.
This reasoning has lead to  propose a relationship between \(\sigma_{\text{los}}\) and \(\sigma\pos\) \citep{2011MNRAS.413..705L}.

In the Figure~\ref{fig:los-vs-pos} that the line-of-sight velocity dispersion is roughly twice the plane-of-sky velocity dispersion.
In the case of homogeneous turbulent velocity we can consider the effect of \textit{project smearing} \citep{1984ApJ...277..556S}, where the projection from three to two dimensions over the line-of-sight depth \(H\), reduces the plane-of-sky amplitude for the condition \(r_{0} < H\).
With a value of \(\sigma\pos / \sigma_{\text{los}}\) = 0.5 we obtain \(r_{0} / H \sim\) 0.02 - 0.1.
This procedure implies depths of the order 10 to 50 times.
In the lower limit \citet{arthur2016turbulence} mentioned the inconsistency for Orion since evidence has show that the emitting layer thickness is of the order of 0.01 - 0.3 pc.
For the most distant regions the previous analysis would give depths of the order of magnitude of the observational box, but considering the analysis using the power-law index (section~\ref{sec:powe-index}) only NGC 595 would comply to this three dimensional structure.

\begin{figure}
\centering 
\includegraphics[width=3in]{Figures/corr-los-vs-pos}
\caption{The $\sigma$-$\sigma_{\text{los}}$ plane. The dotted line represents slope equal to unity.}
\label{fig:los-vs-pos}
\end{figure}

@@

In the section \ref{sec:results} we showed that each \hii{} region of our sample has a turbulent velocity field that can be characterized using the turbulence theory.
The turbulent parameters obtained are unique to each velocity field.
We proceed to develop scaling relations between them and also between the physical properties of each region.

@@

In Section \ref{sec:methods-apply} we mentioned the reduced chi-square method we are using for the determination of the correlation length and the index of the slope. Since this is the first time this method is applied to a sample of HII regions (at least for our knowledge), our results are bounded to be different from previous investigations, including the one that have the same observations as \citet{arthur2016turbulence} and \citet{Melnick:2021x}.

A complete analysis on different emissions lines of the structure function on Orion was carried out by \citet{arthur2016turbulence} and reference therein. 
They observed a tendency that higher ionization lines presents higher values on the magnitude dispersion and the steepness of the structure function slope. 
This results just consider one component on the Gaussian fit. 
The power-law index obtained by \citet{arthur2016turbulence} are \(m \sim 1.2 \pm 0.1\) for \halpha\ and [OIII] emission lines and for [SII] they found \(m \sim 0.8 \pm 0.1\). 
The correlation length for all lines is \(\approx\) 0.05 pc. For the same \halpha\ observation we obtained a value of 1.06$\pm$0.01 and a correlation length of 0.092$\pm$0.007 pc.

>>>>

In Appendix~\ref{sec:finite-box-effects} we consider the effects
on the structure function of the finite size \(L\) of the observational map.
If the true correlation length \(r_0\) is more than a small fraction of the map size
(approximately, \(r_0 > 0.1 L\)),
then the apparent velocity variance \({\sigma'\pos}^2\) measured directly from the data
is less than the true \({\sigma\pos}^2\) of the underlying fluctuations
(see Figure~\ref{fig:finite-box-effect}).
This is because the observed map is not large enough to sample
the full range of velocity variations.
At the same time, the apparent correlation length \(r_0'\) is smaller
than the true value.

@@

In the next sections we discuss the application and interpretation of the turbulent parameters we obtained in our results.
%We present a resume of the turbulence theory and its validation to \hii{} regions.
%It is also mentioned some physical processes that contribute to stirring the ionized gas and the possibility that they are responsible for the observed velocity fluctuations.
We present the most important correlations between the turbulent parameters and physical properties of our \hii{} region sample and finally we discuss our results in the context of previous structure functions.

%\subsection{Turbulence}\label{sec:turbulence-theory}

%\textit{Will 2021-12-10: Moving this section to later for now. Maybe
%  this material could go in discussion.}

%The idea to treat the ionized regions from a fluid mechanic view is intuitive if we consider the continuum hypothesis. 
%We validate this hypothesis using the Knudsen number defined as \(\text{Kn} \equiv \lambda / l\), where \(\lambda\) is the mean free path of the medium and \(l\) a characteristic length of the phenomenon we are studying.
%Taking into account a \(\lambda_{\text{HII}}\) of \SI{2.7e-7}{pc} \citep{1941ApJ....93..369S} and a \(l_{\text{HII}}\) of \SI{1}{pc} for ionized regions we obtained \(\text{Kn} \approx 10^{-7}\), while in general the continuum approach is valid for \(\text{Kn}\ll 1\).

%A turbulent behavior in the flows is more common in fluid systems than a laminar one.
%These turbulent flows tends to be unsteady, irregular and chaotic, and the turbulent motions are observed in many scales. 
%The turbulent flows are associated with a high Reynolds numbers which is defined as \(\text{Re} = l v_{l} / \nu \), where \(v_{l}\) is a characteristic velocity in the fluid system and \(\nu\) is the kinematic viscosity of the medium.
%Experiments have shown that a flow which is laminar become turbulent when increasing the velocity (i.e., increasing the Re) and a large range of velocity fluctuation appear at all scales.
%A high Re reflects high ratio of the advection/difussion terms of the Navier-Stokes equations, being interpreted as that the inertial forces taking over the viscous ones. 
%Hence it is possible to assume that if viscosity is not dominant in a flow, this flow would be turbulent.

%As astronomical observation made it possible to measure a large number of points with a high accuracy, it was found that velocities show a non-thermal component reflecting characteristic of turbulent earthly flows.
%The existence of turbulent flows in astrophysical objects, ranging in scales from 10\(^6\) to 10\(^{17}\) m \citep{2010ApJ...710..853C} is thought to be consequence of the high \(Re\), between 10\(^4\) and 10\(^9\) \citep{1949ApJ...110..329C,lagrois2011} that characterized these objects.

%The classic turbulence theory assumes a three-dimensional isotropic, incompressible and subsonic flow that can be described using an energy spectrum formed by vortices or eddies of different sizes \citep{kolm1}.
%The concept of the energy spectrum assumes that the energy is cascading down inside the flow from the largest to the smallest scales.
%The different scales in the energy cascade are defined based on their Re.
%In one side of the spectrum there is the energy injection scale, \(L_I\), that is related to the largest vortices, called the integral scales, where \(\text{Re} \rightarrow \infty\).
%On the other side of the spectrum there is the dissipation of energy at small scales, \(l_I\), where  \(\text{Re} \rightarrow 1\) and it is assumed that small vortices are responsible for the friction that dissipates the energy flux into thermal energy.
%In between there is the inertial range, \(l_d  << l << L_I\), where in a stationary case the energy transfer is at a constant rate.

%The rate of transfer of specific energy \(\epsilon\) (energy per unit mass) in the inertial range is independent of the \(l\) scale having the form \(\epsilon \sim v_l^2 / \tau_l\), where the kinetic energy is of the order of \( v_l^2\) and the life time of a velocity fluctuation is \(\tau_l\), which can be can be put in terms of \(\tau_l \sim l / v_l\). 
%Hence we obtain \( v_l \sim (\epsilon l)^{1/3}\) where \(\epsilon\) is invariant in the cascade.

%The energy cascade is described using the energy spectrum, $E(k) \propto k^{\beta}$ where \(k\) is the wave number for a determined scale \(l\) ($k \equiv l^{-1}$).
%The total specific energy of a determined $l$ scale is of the order \(\langle v_{l}^{2} \rangle \) and is the energy integral above the associated \(k\), defined as:

%\begin{equation}\label{eq:energy-spectrum}
% \langle v_{l}^{2} \rangle = \int_{k}^{\infty} E(k)dk
%\end{equation}
%
%If it is assumed that this energy is of the order of $(\epsilon l)^{\frac{2}{3}} \sim (\frac{\epsilon}{k})^{\frac{2}{3}}$ we can differentiate equation \ref{eq:energy-spectrum} and obtained the final form:

%\begin{equation}\label{eq:kolmogorov-law}
%E(k) \propto \epsilon^\frac{2}{3} k^{-\frac{5}{3}}
%\end{equation}
%
%where \(\beta = -5 / 3\) is the Kolmogorov law.
%For supersonic turbulence the index is $\beta=-2$ \citep{burg}.

%Using a statistical law that relates the moments \(M_n\) of order \(n\) with the increments in the velocity field for a separation \(\boldsymbol{r}\) \citep{Leqism}, we have:

%\begin{equation}\label{eq:velocity-moments}
%M_n = \langle \vert \boldsymbol{v}(\boldsymbol{x} + \boldsymbol{r})- \boldsymbol{v}(\boldsymbol{x})\vert^n \rangle \propto (\epsilon r)^{n/3}
%\end{equation}
%
%the average is over all the positions \(\boldsymbol{x}\) and directions \(\boldsymbol{r}\). 
%The Kolmogorov model predicts that the moment of order 2, the second-order structure function (equation \ref{eq:Br}), follows \(M_2 \propto r^{2/3}\).

%\subsection{Origins of interstellar turbulence}\label{sec:origins-turbulence}

%In the particular case of GEHR, as supersonic motions dissipate energy by shocks in time scales relatively short compared with the age of the region, it is necessary an energy source to replenish continuously the energy lost. From the observed velocity  dispersion \(\sigma\), and assuming that we have an isotropic distribution of velocities,  we can estimate the 3D velocity dispersion by \(\sigma_\mathrm{3D} = \sqrt{3} \sigma\). The mass of the ionized gas together with the velocity dispersion \(\sigma_\mathrm{3D}\)  are used to estimate the kinetic energy in the GEHRs.
%As these objects have typically  masses of the ionized gas of \num{\sim e5} M\(_{\sun}\) and velocity dispersion values  of \SI{\sim 20}{km.s^{-1}} \citep{1984ApJ...287..116K}, typical kinetic energy of the ionized gas is \SI{\sim e51}{ergs}.

%In the standard Kolmogorov model, the energy spectrum of turbulence becomes dependent only on \(\epsilon\), the mean dissipation of energy per unit time per unit mass of fluid,  with the inertial forces transferring without losses kinetic energy from larger to smaller turbulent elements within the inertial range. Let \(L_c\) be the characteristic length of the largest eddies, and \(\delta v\) the typical velocity.

%We have then that \(\epsilon = (\delta v)^{3}/L\). In steady-state turbulence, equilibrium exists between the energy input and the energy dissipation rates. 
%Although the present observations indicate that turbulence in \hii{} regions may not follow the Kolmogorov model, with energy input occurring at different scales, so that a  truly inertial range may not exist at all, lets us make a crude estimation of the  amount of energy transferred between scales using this simple model. 
%Assuming the above figures for the mass of the gas and velocity dispersion, \(\delta v = \sigma_\mathrm{3D}\),  and a \(L_c\) of \SI{100}{pc}, we obtain that the energy transfer rate \SI{\sim e37}{erg.s^{-1}}, and  the time scale for energy transfer, \(L/\delta v \), would be of few million years.

%There are several energy sources that could provide or contribute  to the energy required: of the order of kpc, the differential rotations of the galaxy that produces shear at large scale, at scales of the order of hundreds of pc, supernova explosions inject a large amount of kinetic energy.
%At scales of several tens of pc the expansion of \hii{} regions and stellar winds are a source of energy and, bipolar flows, shocks, jets and champagne flows inject energy at small scales about one tenth of a pc.

%The lack of precise information on how these mechanism contribute to the emission line broadening make a non-trivial task to determine at what extent they play a role in the interstellar turbulence, contributing to the complexity of the extraction of pure turbulent motions from velocity profiles in nebulae \citep{2011MNRAS.413..705L,arthur2016turbulence}.

@@

Ideally the correlation length \(r_0\) should represent the scale of dominant energy injection.
It is unclear what are the precise mechanisms driving the turbulence in \hii{} regions, thought a lot of options are candidates.
The most probable scenario is that the velocity fluctuations are consequence of the combination of various mechanism.
There are several energy sources that could provide or contribute  to the energy required: of the order of kpc, the differential rotations of the galaxy that produces shear at large scale, at scales of the order of hundreds of pc, supernova explosions inject a large amount of kinetic energy.
At scales of several tens of pc the expansion of \hii{} regions and stellar winds are a source of energy and, bipolar flows, shocks, jets and champagne flows inject energy at small scales about one tenth of a pc.
Many of these mechanisms, at some extent, affect all the \hii{} regions studied in this work.
We can use the kinematic analysis of the regions to investigate how previously identified energy injection mechanisms could be related to the correlation length.

\citet{2009AJ....137..367O} present a three-dimensional study of the dynamic structure of the Orion nebula.
The high-velocity stellar wind from \(\theta^1\) Ori C will confine the ionized gas, even the high ionization emission lines, to a thick shell.
In one direction, at a distance of \SI{0.1}{pc} from the ionizing massive star a stationary shell of shocked material is formed when the ram pressure of the photoevaportation flow balances the thermal pressure of the shocked wind.
In the other direction there is a free flow of the hypersonic wind.
At a smaller scale of \SI{0.02}{pc} there is an interaction between the closest proplyd photoevaporation flow and the stellar wind which results in bowshocks.
According to \citet{2001ApJ...561..830G} the influence of stellar wind interactions is restricted to the central \SI{0.05}{pc}. 
Orion also present a champagne flow where the photoionized gas streams away from the ionization front covering a distance of \SI{\sim 1}{pc} from the molecular cloud \citep{1973ApJ...183..863Z}.

Our correlation length results for the Orion Core and EON from table~\ref{tab:Res}, \num{0.068} y \SI{0.39}{pc} respectively, despite been of the order of the scales mentioned above still aren't conclusive enough to determine a direct relation between them.
As mentioned in \citet{arthur2016turbulence} the mechanism mentioned in the previous paragraph would play a secondary role in stirring up the gas motions and it would be necessary to specify if the velocity fluctuations arise from pure turbulent motion inside the ionized clouds or a consequences of density and brightness fluctuations.

@@

\subsubsection{Structure function power-law index \(m\)}\label{sec:power-index}

The index \(m\) shown in the last column of Table \ref{tab:Res} is used for comparison between observations and the theoretical value of 0.67.
All our indices are above this theoretical value and this is attributed to the fact that the \hii{} regions do not comply with the assumptions established in the development of the turbulent theory.

From section~\ref{sec:regions-milky-way} we know that most of all assumption mentioned in the theory of turbulence are not meet for our \hii{} region sample.
\hii{} regions emerged from a molecular cloud with highly filamentary and clumpy density structure .
There is a large increase in the temperature because of the photoionization, and the density gradients with the pressure gradients accelerate the flow which occurs on multiple scales consequence of the fractal nature of the molecular cloud \citep{arthur2016turbulence}.
The radiation pressure, stellar winds and region expansion, among other physical processes would create pressure-driven shock waves propagating faster than the speed of sound in the medium.
This would make the flow compressible and supersonic in \hii{} regions.
Also, as \hii{} regions are three-dimensional objects our structure function results comes from a projection of this three-dimensional structure to a two-dimensional velocity field.
But despite the complex nature of \hii{} regions and observational limitations we obtain a common pattern for the structure function and the value of the power-law index falls in a certain limited range of values. 
The differences in the power-law index with respect the theoretical value are often used as a diagnostic tools to identify properties that are not consider in the assumptions of the turbulence theory.

To study the projection of a three-dimensional structure function to a two-dimensional structure function, known as projection smoothing \citep{von1951methode, munch1958internal,1964SvA.....8..210K,1987ApJ...317..686O}, relationships between the power-law indices were proposed:

@@

As a conclusion, if the extension of the HII region is compared with its depth (three-dimensional case) the value of the index is \num{1.67}. 
While the case where the extension is much greater than its depth (two-dimensional case) the region will have a value of \num{0.6}.
From Table~\ref{tab:Res} we see that our results fall between these two previous values.

The mean value \(m\) of our sample is \num{\sim 1}. 
Following the equation \ref{eq:projection-smoothing-3d} the \hii{} regions in our sample with \(m >\) 1 would present a depth which is in the order of magnitude comparable to the length of the observed box size \(L\) been closest to this value as \(m\) tends to 1.6. 
On the other hand, \hii{} regions with values \(m <\) 1 would present a thinner structure as they tend to the value of 0.6.
This analysis should not be regarded as conclusive about the true structure of the regions and would require further observations with a combination of kinematics analysis to determine the best way to determine the depth of each region.
As we show in section \ref{sec:sigmapos-vs-sigmalos} the ratio between \(\sigma\pos\) and \(\sigma_{\text{los}}\) can also be used to give an idea of the depth o the region.

@@

As a justification for the use of the structure function we can consider that any relation between the line width and line-of-sight depth can be interpreted in terms of a correlation between velocity spread and scale size.
If we have an optically thin spectral line where it will have a width which is related to the total radial velocity dispersion of all fluctuations sampled along the line-of-sight \citep{1984ApJ...277..556S}. 
The standard deviation of the velocity centroid, \(\sigma\pos\), and the mean non-thermal linewidth, \(\sigma_{\text{los}}\), allow us to compare the relation between the kinematical disorder on the plane-of-the sky and along the line-of-sight  \citep{2011MNRAS.413..705L}.
Considering the previous statements, the structure function is used as a tool to investigate the projection of a three-dimensional correlation function onto the plane of sky \citep{arthur2016turbulence}.

We can consider as a main broadening mechanisms the kinematical disorder along the LOS related to velocity gradients by the clumpiness on the cloud and turbulent movements.
On the plane-of-sky the consequences of those gradients and movements is measured in every pixel. 
The spatial variations on the velocity field would depend on the targeted pixel, at the same time depending on the motions inside the cloud.
This reasoning has lead to  propose a relationship between \(\sigma_{\text{los}}\) and \(\sigma\pos\) \citep{2011MNRAS.413..705L}.

In the Figure~\ref{fig:los-vs-pos} that the line-of-sight velocity dispersion is roughly twice the plane-of-sky velocity dispersion.
In the case of homogeneous turbulent velocity we can consider the effect of \textit{project smearing} \citep{1984ApJ...277..556S}, where the projection from three to two dimensions over the line-of-sight depth \(H\), reduces the plane-of-sky amplitude for the condition \(r_{0} < H\).
With a value of \(\sigma\pos / \sigma_{\text{los}}\) = 0.5 we obtain \(r_{0} / H \sim\) 0.02 - 0.1.
This procedure implies depths of the order 10 to 50 times the correlation length.
In the lower limit \citet{arthur2016turbulence} mentioned the inconsistency for Orion since evidence has show that the emitting layer thickness is of the order of \num{0.01} - \SI{0.3}{pc}.
For the most distant regions the previous analysis would give depths of the order of magnitude of the observational box, but considering the analysis using the power-law index (section~\ref{sec:power-index}) only NGC 595, which index is \num{1.36} would comply to this three dimensional structure.

\begin{figure}
\centering 
\includegraphics[width=3in]{Figures/corr-los-vs-pos}
\caption{The $\sigma$-$\sigma_{\text{los}}$ plane. The dotted line represents slope equal to unity and the dashed line represents a slope of two.}
\label{fig:los-vs-pos}
\end{figure}

@@

In the section \ref{sec:results} we showed that each \hii{} region of our sample has a turbulent velocity field that can be characterized using the turbulence methods despite the results not being as the Kolmogorov model predicts.
The turbulent parameters obtained are unique to each velocity field.
We proceed to develop scaling relations between them and also between the physical properties of each region.

@@

In Section \ref{sec:methods-apply} we mentioned the model we propose for the structure function.
Since this is the first time a model of this type is applied to a sample of HII regions (at least for our knowledge), our results are bounded to be different from previous investigations, including the one that have the same observations as \citet{arthur2016turbulence} and \citet{Medina-Tanco:1997a,Melnick:2021x}.

A complete analysis on different emissions lines of the structure function on Orion was carried out by \citet{arthur2016turbulence}. 
They observed a tendency that higher ionization lines presents higher values on the magnitude dispersion and the steepness of the structure function slope. 
This results just consider one component on the Gaussian fit. 
The power-law index obtained by \citet{arthur2016turbulence} are \(m \sim 1.2 \pm 0.1\) for \halpha\ and [OIII] emission lines and for [SII] they found \(m \sim 0.8 \pm 0.1\). 
The correlation length for all lines is \(\approx\) 0.05 pc. For the same \halpha\ observation we obtained a value of \num{1.07} and a correlation length of \SI{0.068}{pc}.
